The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-21 r_r/manuscript_rihe_r_r.Rmd
submitted r&r mofogit add .git add .

*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities (Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette), 12 selective private liberal arts colleges (Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College), and 15 public research universities (UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, University of Arkansas). We are still trying to figure out what happened.*

@@

Finally, Figure \@ref(fig:south-race-pubu-privhs-pubhs) examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample. Figure \@ref(fig:south-race-privu-privhs-pubhs) does the same for selective private universities. These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504]. For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools. This was true for most public universities in our sample, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati. A notable exception is SUNY Stony Brook, though this university only visited 12 private universities in the South. Results for selective private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) (with the exception of Marquette) mirror the results for public research universities. Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits. Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private schools in the South.

>>>>

*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.] We are still trying to figure out what happened.*

@@

Finally, Figure \@ref(fig:south-race-pubu-privhs-pubhs) examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample. Figure \@ref(fig:south-race-privu-privhs-pubhs) does the same for selective private universities. These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504]. For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools. This was true for all universities in our sample that visited a substantial number of schools in the South, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati. Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits. Results for private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) are very similar, with Emory, Northwestern, and Case Western visiting private schools with a low share of Black/Latinx/Native students. Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private schools in the South. For most universities that made a substantial number of visits in the South, white students comprised around 70% of total enrollment at visited private schools compared to around 40% at visited public schools.
